Shallow EDSLs and Object-Oriented Programming

### 2018-09-29 Programming19/Main.tex
Add ccs

%% for comments
\input{Preamble}

% Document starts
\begin{document}

>>>>

%% for comments
\input{Preamble}
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008.10011024</concept_id>
<concept_desc>Software and its engineering~Language features</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011050.10011017</concept_id>
<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Language features}
\ccsdesc[500]{Software and its engineering~Domain specific languages}
% Document starts
\begin{document}
